Bare Demo of IEEEtran.cls for Journals

### 2019-12-08 2-oracle/report/paper.tex
write some part for experiments

We use a simple stochastic gradient descent optimizer to train the network on the 9120 training samples and validate it on the remaining 400 samples.

@@

\section{Experiments}
\subsection{Test Set}
\subsection{Results}

>>>>

We use a simple stochastic gradient descent optimizer to train the network on the 9120 training samples and validate it on the remaining 400 samples.
The data has been normalized into the range from 0 to 1.

@@

\section{Experiments}
Then we test the accuracy of our models under more realistic circumstances.

\subsection{Test Set}
We test models on our homebrew dataset where we write oracle bone characters using different pens, on different papers, and captured under different lighting condition.
Figure~\ref{fig:testset} shows samples in the test set.
We can see that the background color and character color varies dramatically from those of the original dataset.
Moreover, there are other noises such as the texture of the paper that could disturb our models.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.19\linewidth]{fig/testset/test_bxy_2_30.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_lcx_1_40.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_ljy_2_28.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_wzy_1_30.jpg}
	\includegraphics[width=0.19\linewidth]{fig/testset/test_xsn_2_28.jpg}
	\caption{Samples in Test Set}
	\label{fig:testset}
\end{figure}

There are 400 samples in the test set, 10 samples for each micro category.
We only write 200 samples and double the size by capturing them under different lighting.

\subsection{Evaluation and Improvements}
To recognize characters in the test set, we need to first preprocess the samples.

We first obtain the grey scale version of the images.
For the test on the neural network, we normalize images as before and set pixels with values less than some threshold $\delta$ to 0.
For the test on the template matching, we do not normalize images but set pixels with values less than some threshold $\Delta$ to 0.
In this way, we can remove the influence of the background color on the recognition result.

\begin{table}[h]
	\centering
	\caption{Accuracy for Different Models}
	\label{tab:result}
	\begin{tabular}{|c|c|c|}
		\hline
		& Cat10 & Cat40 \\\hline
		DNN ($\delta=0.5$) & 0.8475 & 0.5275 \\\hline
		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56 \\\hline
		TM ($\Delta=?$) & ? & ? \\\hline
		TM Ensemble ($\Delta=?$) & ? & ? \\\hline
	\end{tabular}
\end{table}

Table~\ref{tab:result} shows the accuracy of different models wrt. the test set.
